Application-Level Regression Testing Framework using Jenkins

### 2017-03-28 manuscript/manuscript.tex
Clean up previously commented out / incorporated sections; moved some texts to conclusion (will rework more on this later).

In this paper we describe in details our experience in using Jenkins to perform application-level regression testing on high-performance computing systems such as the Blue Water supercomputer at the National Center for Supercomputing Applications (NCSA), Darter and Beacon at the National Institute for Computational Sciences (NICS). These systems are Cray XE, XK, XC, and CS series. The outline of this paper is as follows. [FIXME: WRITE PAPER OUTLINE AFTER COMPLETE DRAFT]

%Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance. Another requirement was to find an automated solution for running a suite of test jobs that reveal the system health after upgrades and outages before returning the system to service.

@@

% \subsection{Introduction to Jenkins}
% Jenkins [2] is a self-contained, open source automation server which can be used to automate all sorts of tasks such as building, testing, and deploying software. Jenkins can be installed through native system packages, Docker, or even run standalone by any machine with the Java Runtime Environment installed. 
% To install from rpm as root for centos:
% \begin{lstlisting}
% wget -O /etc/yum.repos.d/jenkins.repo \
%   http://pkg.jenkins-ci.org/redhat-stable/jenkins.repo
% rpm --import \
%   https://jenkins-ci.org/redhat-stable/jenkins-ci.org.key
% yum install jenkins
% \end{lstlisting}

@@

%\subsection{Master-Node Configuration}
%We added a standard user account to our cluster that will execute the Jenkins tests. Unique ssh keys were generated on the Jenkins Server for accessing the user account on production and test environments.  The keys on the server are located in Jenkins home directory (/var/lib/jenkins/.ssh). Using the GUI management console, the keyfile location and passphrase was entered under Manage Jenkins, Configure System, SSH remote hosts section. A unique SSH site is configured for our TDS, production and development login nodes.

%\subsection{Accessing Login Nodes}
%The ssh public key generated on Jenkins Server was deployed in the login node user account. The login node sshd_config was modified to allow Public Key Authentication from the Jenkins Server IP.

@@

% FIXME: CONSIDER DELETING THIS SECTION SINCE IT HAS BEEN INCORPORATED ABOVE
%\subsection{Master-Node Configuration NCSA}
%We added a standard user account to our Blue Waters environment that will execute the Jenkins projects. Unique ssh keys were generated on the Jenkins Server for accessing the user account on production and test environments.  The keys on the server are located in Jenkins home directory (/var/lib/jenkins/.ssh). Using the GUI management console, the keyfile location and passphrase were entered under Manage Jenkins, Configure System, SSH remote hosts section. A unique SSH site is configured for our test and development (TDS) CRAY, production and development login nodes.

% FIXME: REWORK / INCORPORATE THIS SECTION FOR BETTER FLOW
\subsection{Accessing Login Nodes NCSA}
The ssh public key generated on Jenkins Server was deployed in the login node user account. The login nodes sshd_config was modified to allow Public Key Authentication from the Jenkins Server IP. We typically run the latest Programming Environment (PE) on our TDS. Our production login nodes and the supercomputer have the latest PE installed as non default during initial testing and it can be loaded by modulefile selection. Our test login node (Bright Cluster Provisioned EsLogin) is utilized for testing new software stacks and changes to the login environment that are independent of our production resources. Therefore Jenkins Projects tailored for each environment allow for regression testing of the current production as well as pre-production user-level environments.

%\subsection{Master-Node Configuration NICS}
%\subsection{Accessing Login Nodes NICS}

@@

\section{Conclusion}
\subsection{reproducibility and regression testing}
Jenkins provides the framework we need to maintain tests in a consistent fashion and track the results over time (logs and plots ).  Tests typically are not changed so that we get apples-apples comparisons.  When a new test is needed for a particular activity, we attempt to derive it from an existing test to maintain consistency and simplify test creation.  Reusable test components (watchdog scripts, plotting metrics) are employed to make construction of completely new tests straightforward.
\subsection{rapid reaction}
The notification feature keeps test owners engaged in the testing activity of Jenkins and they are often our first responders to system issues.  This results in a shorter reaction time when the system is not performing to expectations--staff are notified automatically when the user experience is impacted.
\subsection{caveats}
\subsubsection{transient errors}
Transient errors with Jenkins sometimes occur--particularly with the Jenkins ssh subsystem.  It's not unusual to get ssh failure rates of 1/100 which are completely transient (immediately running the test again manually clears the issue on the dashboard).
\subsubsection{test scale and frequency}
There is some subjectivity in the frequency and scale (resource utilization) of tests.  Testing too often, too large, or some combination of the two may perturb the system such that other tests are impacted or create bottlenecks in the system for the real user community.  This is the primary reason we require peer review for new tests.
\label{sec:conclusion}

>>>>

In this paper we describe in details our experience in using Jenkins to perform application-level regression testing on high-performance computing systems such as the Blue Water supercomputer at the National Center for Supercomputing Applications (NCSA), Darter and Beacon at the National Institute for Computational Sciences (NICS). These systems are Cray XE, XK, XC, and CS series. The outline of this paper is as follows. [FIXME: WRITE PAPER OUTLINE AFTER COMPLETE DRAFT].

@@

@@

@@

@@

\section{Conclusion}
\label{sec:conclusion}

We typically run the latest Programming Environment (PE) on our TDS. Our production login nodes and the supercomputer have the latest PE installed as non default during initial testing and it can be loaded by modulefile selection. Our test login node (Bright Cluster Provisioned EsLogin) is utilized for testing new software stacks and changes to the login environment that are independent of our production resources. Therefore Jenkins Projects tailored for each environment allow for regression testing of the current production as well as pre-production user-level environments.

\subsection{reproducibility and regression testing}
Jenkins provides the framework we need to maintain tests in a consistent fashion and track the results over time (logs and plots ).  Tests typically are not changed so that we get apples-apples comparisons.  When a new test is needed for a particular activity, we attempt to derive it from an existing test to maintain consistency and simplify test creation.  Reusable test components (watchdog scripts, plotting metrics) are employed to make construction of completely new tests straightforward.
\subsection{rapid reaction}
The notification feature keeps test owners engaged in the testing activity of Jenkins and they are often our first responders to system issues.  This results in a shorter reaction time when the system is not performing to expectations--staff are notified automatically when the user experience is impacted.
\subsection{caveats}
\subsubsection{transient errors}
Transient errors with Jenkins sometimes occur--particularly with the Jenkins ssh subsystem.  It's not unusual to get ssh failure rates of 1/100 which are completely transient (immediately running the test again manually clears the issue on the dashboard).
\subsubsection{test scale and frequency}
There is some subjectivity in the frequency and scale (resource utilization) of tests.  Testing too often, too large, or some combination of the two may perturb the system such that other tests are impacted or create bottlenecks in the system for the real user community.  This is the primary reason we require peer review for new tests.
